Reproduce anaylses of Beninca et al (2008)

### 2016-02-12 code/report.Rmd
comment LE indirect method

## don't run this unless you have some time (it takes a while)
LE <- Get_GLE_Beninca(X)
save(LE, file="~/Desktop/GLE_estimate.Rdata")

## load the already saved data from github (this can take some time depending on the internet connection)
#source_data(paste0(repo, "/data/GLE_estimate.Rdata?raw=True"))

>>>>

## don't run this unless you have some time (it takes a while)
#LE <- Get_GLE_Beninca(X)
#save(LE, file="~/Desktop/GLE_estimate.Rdata")

## load the already saved data from github (this can take some time depending on the internet connection)
source_data(paste0(repo, "/data/GLE_estimate.Rdata?raw=True"))
